---
title: 'Jim Wright CV'
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [anderson-cv.css]
    number_sections: false
links-to-footnotes: false
# knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

#### cv entries #####
cv_entries <- readxl::read_xlsx(here::here("data", "cv_entries.xlsx"))

#### publications #####
pubs <- readxl::read_xlsx(here::here("data", "pubs.xlsx")) %>% 
  arrange(order) %>% 
  select(-order)

pubs <- map_df(pubs, ~gsub("\\.$", "", .x))

courses <- readxl::read_xlsx(here::here("data", "courses.xlsx"))

```


```{r}
PDF <- FALSE # Set to TRUE when rendering to PDF via pagedown::chrome_print()
if(PDF) {
  header <- '
  View online
  <a href="https://jim-wright90.github.io/wright_cv/" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a>
  '
} else {
  header <- '
  Download PDF
  <a href="https://github.com/jim-wright90/wright_cv/raw/main/index.pdf" class="icon-block">
      <i class="fas fafooter fa-download"></i>
  </a>
  '
}
```

<div class = "download">
```{r results = "asis"}
cat(header)
```

</div>

<div class = "footer",>
  <a href="https://github.com/Jim-Wright90" class="icon-block">
      <i class="fab fafooter fa-github"> | </i>
  </a>
  
   <a href="mailto:jjwright90@gmail.com" class="icon-block">
      <i class="fas fafooter fa-envelope"> | </i>
  </a>  
  
   <a href="mailto:jim.wright@marzanoresearch.com" class="icon-block">
      <i class="fas fafooter fa-envelope"> | </i>
  </a>  
  
  <a href="mailto:jwrigh16@uoregon.edu" class="icon-block">
      <i class="fas fafooter fa-envelope"> | </i>
  </a> 
  
  <a href="https://www.linkedin.com/in/jim-wright-a944698b/" class="icon-block">
      <i class="fab fafooter fa-linkedin"></i>
  </a>  
  
  <a href="https://orcid.org/my-orcid?orcid=0000-0003-3035-7003" class="icon-block">
      <i class="fab fafooter fa-orcid"></i>
  </a>
  
  
</div>


<div id = "block_container">

<div class = "first", id="bloc1">Jim</div>  
<div class = "last", id="bloc2">Wright</div>

</div>

<div id = "position", class = "position">
Researcher at Marzano Research and Clinical Supervisor at the University of Oregon Department of Communication Disorders and Sciences
</div>


<div id = "sub", class = "sub">
Curriculum Vita
</div>


<div class="grid-container">

```{r summary, child = here::here("content", "summary.Rmd")}
```

```{r contact-info, child = here::here("content", "contact-info.Rmd")}
```

</div>

# Professional Background

<div class = "inote">
Icons link to additional content  
</div>

## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
         what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what)
         ) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Career History {.history .nohead}

```{r}
cv_entries %>% 
  filter(type == 'history') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>%
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what, additional_info) %>% 
  kable()
```


## Selected Project Experience

```{r}
cv_entries %>% 
  filter(type == 'project') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
    what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what)) %>%
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what, role, additional_info) %>% 
  kable(col.names = NULL)


# cv_entries %>% 
#   filter(type == 'education') %>% 
#   mutate(what = paste0(what, ", ", where),
#          what = gsub("NA", "", what),
#          what = gsub(", $", "", what),
#          what = ifelse(!is.na(url), 
#                        paste0("[", what, "](", url, ")"), 
#                        what)
#          ) %>% 
#   mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
#   select(year, what) %>% 
#   kable()
```

## Graduate Student Research Experience 

```{r}
cv_entries %>% 
  filter(type == 'student_research') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what, additional_info) %>% 
  kable(col.names = NULL)
```

I consulted with HCAMP to complete my capstone project in order to obtain the data science specialization from the University of Oregon. Our collaboration focused on retrospectively analyzing ImPACT test scores and PCSS severity ratings. Data products I produced for HCAMP are accessible [here](https://jim-wright90.shinyapps.io/HCAMP_shiny/?_ga=2.184615983.768699848.1629757508-733798040.1613499824) and [here](https://jim-wright90.github.io/hcamp_clusters/).

## Graduate Student Teaching Experience 

```{r}
cv_entries %>% 
  filter(type == 'student_teaching') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable(col.names = NULL)
```

## Graduate Student Service 

```{r}
cv_entries %>% 
  filter(type == "student_service") %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what, additional_info) %>% 
  kable(col.names = NULL)
```

## Professional Affiliations 

```{r}
cv_entries %>% 
  filter(type == "professional_affiliation") %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable(col.names = NULL)
```

## Certification and Licensure 

```{r}
cv_entries %>% 
  filter(type == "certification_licensure") %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable(col.names = NULL)
```

## Professional Training 

```{r}
cv_entries %>% 
  filter(type == "professional_training") %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable(col.names = NULL)
```

## Programming Skills

```{r}
cv_entries %>% 
  filter(type == "programming_skill") %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable(col.names = NULL)
```


# Teaching 

<div class = "inote">
Icons link to additional content  
</div>

## Courses Taught

All courses taught at the University of Oregon Department of Communication Disorders & Sciences.

```{r}
courses %>% 
  filter(type == "cds") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website),
                         paste0(
                           '[<i class="fas falink fa-globe"></i>](',
                           website,
                           ')'
                         ),
                         ""),
         fa_git = ifelse(!is.na(repo),
                         paste0(
                           '[<i class="fab falink fa-github"></i>](',
                           repo,
                           ')'
                         ),
                         ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""), 
                         credits, " credit hours.<sp></sp>",
                         fa_git, "<sp></sp>", fa_web),
         order = paste0(order, ".")) %>%
  select(order, course) %>%
  kable(col.names = NULL)
```

# Scholarship

<div class = "inote">
Icons link to additional content  
</div>

## Peer-Reviewed Publications

```{r}
make_cite <- function(authors,	year,	title,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL,
                      book = NULL, place_published = NULL, conference = NULL,
                      poster = NULL, conf_loc = NULL, annual_meeting = NULL,
                      version = NULL,...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*.")
  }
  
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), "(", issue, "),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0("[doi: ", doi, "](", url, ")")
  }
  if(!is.null(pages)) {
    if(!is.null(book)) {
      pages <- paste0("(pp. ", pages, ").")
    }
    else {
     pages <- paste0(pages,".") 
    }
  }
  if(!is.null(book)) {
    book <- paste0("*", book, "*")
  }
  if(!is.null(conference)) {
    title <- paste0("*", title, "*")
    if(is.null(poster)) {
      if(annual_meeting) {
        conference <- paste0("Presentation at the annual ", conference, ".")
      }
      else {
        conference <- paste0("Presentation at the ", conference, ".")
      }
    }
    else if(poster) {
      if(annual_meeting) {
       conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference,
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Poster presented at the ", 
                             conference, 
                             ", ", 
                             conf_loc, 
                             ".") 
      }
    }
    else {
       if(annual_meeting) {
          conference <- paste0("Paper presented at the annual meeting of the ", 
                            conference, 
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Paper presented at the ", 
                             conference, 
                             ",", 
                             conf_loc,
                            ".") 
      }
    }
  }
  if(!is.null(version)) {
    version <- paste0("R package version ", version, ".")
  }
  authors <- gsub(
    "Wright, J\\.?",
    "<span style= 'font-weight: 500'>Wright, J.</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        paste0(title, "."),
        version, 
        conference,
        journal, 
        volume,
        book,
        pages, 
        doi,
        place_published)
}

prpas <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

each_cite <- split(prpas, seq_len(nrow(prpas)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_doc <- ifelse(
  !is.na(prpas$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prpas$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prpas$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prpas$git_repo, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prpas$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 

pubs_tbl <- pubs_tbl %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)
```

<!-- <div class = "hangingindent prpa nohead"> -->

```{r} 
kable(pubs_tbl[1:9, ],
      col.names = NULL)
```


```{r} 
# kable(pubs_tbl[10:nrow(pubs_tbl), ])
```

## Professional Reports

```{r}
reports <- pubs %>% 
  filter(type == "mzr_report") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(reports$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(reports$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(reports$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(reports, seq_len(nrow(reports)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

reports_tbl <- tibble(year = reports$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc, 
                                 fa_pres, 
                                 fa_git)
)
  

reports_tbl <- reports_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)
```

<!-- <div class = "hangingindent prpa nohead"> -->

```{r} 
kable(reports_tbl[1:9, ],
      col.names = NULL)
```



## Professional Presentations 

<!-- <div class = "hangingindent prpa nohead"> -->

```{r}
confs <- pubs %>% 
  filter(type == "conference") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(confs$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(confs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(confs$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(confs, seq_len(nrow(confs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

conf_tbl <- tibble(year = confs$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc, 
                                 fa_pres, 
                                 fa_git)
)
  

conf_tbl <- conf_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

# kable(conf_tbl[1:7, ])
```

```{r}
kable(conf_tbl[1:7, ],
      col.names = NULL)
```



```{r}
# kable(conf_tbl[8:18, ])
```





```{r}
# kable(conf_tbl[19:28, ])
```





```{r}
# kable(conf_tbl[29:nrow(conf_tbl), ])
```

# Honors and Awards {.submitted .nohead}

<div class="hangingindent">

```{r}
cv_entries %>%
  filter(type == "award") %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(what, ". (", year_end, "). ", 
                       ifelse(!is.na(additional_info), 
                              paste0(additional_info, "."),
                              "")
                       )
        ) %>%
  select(count, cite) %>%
  kable()
```